---
output:
  html_document:
    theme: flatly
    df_print: kable
    toc: true
    toc_float: true
    toc_depth: 2
always_allow_html: true
params:
  inc_igvreport: false
  igv_report: null
---
<style type="text/css">
  /* KiTZ brand palette: #0047b9 blue and #ff5c00 orange are taken from the
     KiTZ logo; the categorical pair is validated for colour-vision deficiency. */
  :root {
    --primary:            #0047b9;   /* KiTZ blue - headings, table headers */
    --primary-dark:       #28348a;   /* KiTZ navy */
    --primary-container:  #dce6f7;   /* tinted panels, hover rows */
    --on-primary:         #ffffff;
    --accent:             #ff5c00;   /* KiTZ orange - second data series */
    --surface:            #ffffff;
    --surface-variant:    #f5f7fa;
    --on-surface-variant: #49454f;
    --outline:            #ccd6e5;
    --warning:            #ff5c00;
    --error:              #c61826;   /* KiTZ red */
  }

  /* System stack: the report is rendered --self-contained, so web fonts cannot
     be fetched. These are humanist sans faces present on each platform. */
  body{
  font-size: 12pt;
  line-height: 1.6;
  text-align: left;
  color: #222;
  font-family: "Segoe UI", system-ui, -apple-system, "Helvetica Neue",
               Roboto, "Noto Sans", Arial, sans-serif;
  font-variant-numeric: tabular-nums;
  }

  /* rmarkdown caps the content column at ~940px; widen it so the coverage and
     copy-number figures have room */
  .main-container {
    max-width: 1360px;
    margin-left: auto;
    margin-right: auto;
  }
  img { max-width: 100%; height: auto; }

  /* prose that used to be marked up as h4 headings */
  .note {
    font-size: 1em;
    margin: 0 0 14px 0;
  }
  .note-muted {
    font-size: 0.9em;
    color: #555;
    margin: 0 0 8px 0;
  }
  .contact { font-size: 0.9em; margin: 2px 0; }

  /* title + sample details on the left, logos on the right, one baseline */
  .report-header {
    display: flex;
    align-items: center;
    justify-content: space-between;
    gap: 32px;
    padding-bottom: 18px;
    margin-bottom: 24px;
    border-bottom: 1px solid var(--outline);
  }

  .report-header .titles { flex: 1 1 auto; min-width: 0; }

  .report-header .logos {
    display: flex;
    align-items: center;
    gap: 24px;
    flex: 0 0 auto;
  }

  /* the title sits inside the header row, so drop the section rule above it */
  .report-header h2 {
    border-top: none;
    margin: 0 0 10px 0;
    padding-top: 0;
  }

  .logo {
    height: 84px;
    width: auto;
  }

  .sample-info {
    font-size: 12pt;
    color: #555;
    margin: 0;
  }

  @media (max-width: 900px) {
    .report-header { flex-direction: column; align-items: flex-start; }
  }
  
  .smaller-text {
    font-size: 0.85em;
  }
  
  .footer {
    text-align: center;
    font-style: italic;
    font-size: 12px;
    color: #666;
    border-top: 1px solid #ccc;
    padding: 10px;
    margin-top: 20px;
  }
  
  .research-warning {
    background-color: #ffebee;
    border: 2px solid #f44336;
    color: #d32f2f;
    padding: 20px;
    text-align: center;
    font-size: 18px;
    font-weight: bold;
    margin: 20px 0;
    border-radius: 5px;
  }
  
  /* only real section headings get the rule and spacing */
  h1, h2, h3 {
    color: var(--primary);
    font-weight: 600;
    margin-top: 40px;
    margin-bottom: 16px;
    padding-top: 20px;
    border-top: 1px solid #e6e6e6;
  }

  h1:first-child, h2:first-child, h3:first-child {
    border-top: none;
    margin-top: 20px;
  }

  h4 { font-size: 1.05em; font-weight: 600; margin: 18px 0 6px 0; }

  p {
    margin-bottom: 10px;
  }

  /* tables - primary header, alternating surface rows, thin outline grid */
  table.table {
    font-size: 0.9em;
    border: 1px solid var(--outline);
    font-variant-numeric: tabular-nums;   /* numeric columns line up */
  }
  /* the child-combinator form outranks bootstrap's .table>thead>tr>th, which is
     injected after this block and would otherwise win the tie */
  table.table > thead > tr > th {
    background-color: var(--primary);
    color: var(--on-primary);
    font-weight: 600;
    border-bottom: none;
    vertical-align: middle;
  }
  table.table > tbody > tr > td { border-top: 1px solid var(--outline); }
  table.table-striped > tbody > tr:nth-of-type(odd)  > td { background-color: var(--surface); }
  table.table-striped > tbody > tr:nth-of-type(even) > td { background-color: var(--surface-variant); }
  table.table-hover > tbody > tr:hover > td { background-color: var(--primary-container); }

  .experimental {
    background-color: #fff6ef;
    border-left: 4px solid var(--warning);
    padding: 14px 18px;
    margin: 18px 0;
    border-radius: 3px;
  }
  .experimental .small { font-size: 0.85em; color: var(--on-surface-variant); }

  hr.plot-sep {
    border: 0;
    border-top: 1px dashed var(--outline);
    margin: 28px 0 18px 0;
  }

  .igv-frame {
    width: 100%;
    height: 700px;
    border: 1px solid var(--outline);
    border-radius: 3px;
    background: #fff;
  }

  .section {
    margin-bottom: 10px;
    padding-bottom: 10px;
  }
  
  .smaller-text h4 {
    margin-top: 0px;
    margin-bottom: 0px;
    padding-top: 0px;
    padding-bottom: 0px;
    line-height: 1.0;
  }
  
  .smaller-text p {
    margin-bottom: 0px;
    line-height: 1.0;
  }
  
  /* references + contact: a distinct closing block, separated from the last
     figure by a rule and its own tinted surface */
  .contact-section {
    margin-top: 56px;
    padding: 24px 28px 20px 28px;
    border-top: 3px solid var(--primary);
    background-color: var(--surface-variant);
    border-radius: 4px;
  }

  .contact-section .note-muted { margin-bottom: 10px; }

  /* clear gap between the references above and the contact block below */
  .contact-section .contact:first-of-type {
    margin-top: 32px;
    padding-top: 24px;
    border-top: 1px solid var(--outline);
  }
  .contact-section .contact { line-height: 1.7; }
</style>

```{r logo_paths, echo=FALSE, results='asis'}
# Embed logos as base64 data URIs. An absolute container path in <img src>
# resolves only inside the container, so the delivered HTML would show broken
# images anywhere else.
embed_png <- function(candidates) {
  for (p in candidates) {
    if (file.exists(p)) {
      return(paste0("data:image/png;base64,", base64enc::base64encode(p)))
    }
  }
  warning("Logo not found in any of: ", paste(candidates, collapse = ", "))
  ""
}
rapid_logo_path <- embed_png(c("/opt/logos/rapid_cns2_logo.png",
                               "logos/rapid_cns2_logo.png",
                               "rapid_cns2_logo.png"))
ukhd_logo_path  <- embed_png(c("/opt/logos/ukhd_logo.png",
                               "logos/ukhd_logo.png",
                               "ukhd_logo.png"))
```

<div class="research-warning">
  RESEARCH USE ONLY
</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(ggplot2)
```


<div class="section">

<div class="report-header">
<div class="titles">

## **Rapid-CNS^2^ report**

<div class="sample-info">
**Sample ID:** `r sample`  
**Patient:** `r patient`
</div>

</div>
<div class="logos">
  <img src="`r rapid_logo_path`" alt="Rapid-CNS² Logo" class="logo">
  <img src="`r ukhd_logo_path`" alt="Institution Logo" class="logo">
</div>
</div>

<div class="note">
**Method.** Frozen tumour tissue was processed with the Oxford Nanopore SQK-LSK114
ligation sequencing kit, with adaptive sampling enriching for 160 gene regions of
the NPHD panel. Reads were analysed with the Rapid-CNS^2^ Nextflow pipeline
(`r software_ver`), covering single-nucleotide and structural variants, copy
number, genome-wide methylation-based classification and MGMT promoter status.
</div>
<div class="note-muted">
**Research use only.** Rapid-CNS^2^ is under active development and has not been
clinically validated in sufficiently large cohorts. Interpretation of these results
in a clinical setting, and any action taken on them, remain the sole responsibility
of the treating physician.
</div>

</div>

<div class="section">

## On-target coverage
```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width=13, fig.height=5, out.width="100%"}
df <- read.delim(coverage)
# mosdepth writes 'total' and 'total_region' summary rows; they are not
# chromosomes and would appear as a spurious bar on the x axis.
df <- df[!grepl("^total", df$chrom), ]
df$Reads <- "All"
df$Reads[endsWith(df$chrom,"_region")] <- "On_target"
df$chrom <- gsub("_region","",df$chrom)
df$mean <- as.numeric(df$mean)
df$chrom[df$chrom=="chr1"] <- "chr01"
df$chrom[df$chrom=="chr2"] <- "chr02"
df$chrom[df$chrom=="chr3"] <- "chr03"
df$chrom[df$chrom=="chr4"] <- "chr04"
df$chrom[df$chrom=="chr5"] <- "chr05"
df$chrom[df$chrom=="chr6"] <- "chr06"
df$chrom[df$chrom=="chr7"] <- "chr07"
df$chrom[df$chrom=="chr8"] <- "chr08"
df$chrom[df$chrom=="chr9"] <- "chr09"

df <- df[order(df$chrom),]

# KiTZ blue / orange: validated as a colourblind-safe categorical pair
ggplot(df, aes(x=chrom, y=mean, fill=Reads)) +
  geom_bar(stat="identity", position=position_dodge(width=0.8), width=0.7) +
  theme_classic(base_size = 12) +
  theme(axis.text.x     = element_text(angle = 45, hjust = 1),
        axis.line       = element_line(colour = "#ccd6e5"),
        axis.ticks      = element_line(colour = "#ccd6e5"),
        panel.grid.major.y = element_line(colour = "#eef1f5"),
        legend.position = "top",
        legend.title    = element_blank()) +
  ylab("Mean coverage") +
  xlab("Chromosome") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  scale_fill_manual(values = c("All" = "#0047b9", "On_target" = "#ff5c00"))
```

</div>

<div class="section">

## Mutations
```{r, echo=FALSE}
if (file.exists(mutations)) {
  mutations_df <- read.csv(mutations)
  if (nrow(mutations_df) > 0) {
    # row_spec(0) styles the header inline; a stylesheet rule loses to the
    # bootstrap theme, which is injected after this document's <style> block
    kable(mutations_df, format = "html", escape = FALSE) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = TRUE, font_size = 12) %>%
      row_spec(0, bold = TRUE, color = "white", background = "#0047b9") %>%
      scroll_box(width = "100%", height = "600px",
                 box_css = "border: 1px solid #ccd6e5; padding: 4px; ")
  } else {
    cat("No mutations found.")
  }
} else {
  cat("Mutations file not found.")
}
```

</div>

<div class="section">

## IGV Report

```{r, echo=FALSE, results='asis', eval=inc_igvreport}
# Only a placeholder here. The IGV report is a standalone document of ~100 MB of
# embedded read data; feeding it to pandoc is slow and it gets escaped to text,
# because pandoc reads its blank lines as ending the raw HTML block. make_report.R
# splices it into an iframe in the rendered file instead.
cat('<div id="igv-embed"></div>')
```

</div>

<div class="section">

## Copy number profile

#### Read depth (CNVpytor)

<div class="note-muted">
Read-depth copy number in 100 kb bins; each point is the normalised depth of one
bin relative to the genome-wide mean, so gains sit above and losses below the
central band.
</div>

```{r, echo=FALSE, warning=FALSE, out.width="100%"}
knitr::include_graphics(cnv_plot)
```

```{r, echo=FALSE, results='asis'}
if (!exists("savana_cnv_plot")) savana_cnv_plot <- NULL
if (!is.null(savana_cnv_plot)) {
  cat('<hr class="plot-sep">\n')
  cat('<h4>Absolute copy number (SAVANA)</h4>\n')
  cat('<div class="note-muted">',
      'Fitted from read depth',
      'and B-allele frequency and corrected for tumour purity and ploidy. The',
      'y axis is copy number rather than a ratio, the dashed line marks the',
      'sample ploidy, and CNS-relevant genes are annotated at their copy number',
      '(\u25b3 = above the axis limit).',
      '</div>\n')
}
```

```{r, echo=FALSE, warning=FALSE, out.width="100%"}
if (!is.null(savana_cnv_plot)) knitr::include_graphics(savana_cnv_plot)
```

```{r, echo=FALSE, results='asis'}
if (!exists("purity_ploidy")) purity_ploidy <- NULL
if (!is.null(purity_ploidy) && nrow(purity_ploidy)) {
  pp <- purity_ploidy[1, , drop = FALSE]
  cat('<div class="experimental">',
      '<strong>Predicted tumour purity and ploidy (experimental)</strong><br>',
      sprintf('Purity <strong>%s%%</strong> &nbsp;&middot;&nbsp; Ploidy <strong>%s</strong>',
              round(as.numeric(pp$purity) * 100), round(as.numeric(pp$ploidy), 2)),
      '<br><span class="small">Estimated by SAVANA from read depth and B-allele',
      'frequency. This estimate is <strong>experimental and not validated</strong>',
      'for clinical use; consult the SAVANA manuscript and repository',
      '(<a href="https://github.com/cortes-ciriano-lab/savana">github.com/cortes-ciriano-lab/savana</a>)',
      'for method details and limitations.</span>',
      '</div>\n')
}
```
</div>

<div class="section">

```{r, echo=FALSE}
oob <- read.delim(rf_details, header = FALSE, sep = ":")
rf_val <- function(key, default = NA) {
  i <- which(trimws(oob[[1]]) == key)
  if (length(i)) trimws(oob[[2]][i[1]]) else default
}
n_450k    <- as.integer(rf_val("450k_overlap"))
n_feature <- as.integer(rf_val("Training_probes"))
# ranger reports the Brier score in $prediction.error for probability forests.
# Older rf_details files label it OOB_error.
brier <- as.numeric(rf_val("Brier_score", rf_val("OOB_error")))
mc <- read.delim(votes, sep = " ")
```

## Rapid CNS^2^ methylation classification
<div class="note">
Methylation-based classification used `r n_feature` CpG features selected from `r n_450k` sites overlapping the HM450 array. The Brier score of this ad-hoc classifier is `r paste0(round(brier*100,digits=1),"%")`. Using this classifier, the sample has been classified as  **`r rownames(mc[which.max(mc$Recalibrated_Frequency),])`**. This prediction has a confidence score of **`r paste0(round(as.numeric(mc$Recalibrated_Frequency[which.max(mc$Recalibrated_Frequency)]),digits=1),"%")`**. The calibrated score distribution for the Top 10 entities is given below.
</div>

```{r,echo=FALSE,warning=FALSE, fig.pos="h"}
mc$methClass <- rownames(mc)
# single series: one hue, no legend, recessive axes
ggplot(data=mc, aes(x=methClass, y=Recalibrated_Frequency)) +
  geom_bar(stat="identity", fill="#0047b9", width=0.7) +
  coord_flip() +
  scale_x_discrete(limits=mc[order(mc$Recalibrated_Frequency,decreasing=T),]$methClass[10:1]) +
  scale_y_continuous(limits=c(0,100), expand = expansion(mult = c(0, 0.05))) +
  ylab("confidence score (%)") + xlab("methylation class") +
  theme_classic(base_size = 12) +
  theme(aspect.ratio     = 1,
        text             = element_text(family="sans"),
        axis.line        = element_line(colour = "#ccd6e5"),
        axis.ticks       = element_line(colour = "#ccd6e5"),
        panel.grid.major.x = element_line(colour = "#eef1f5"))

```

</div>

<div class="section">

## MNP-Flex classification

```{r, echo=FALSE, results='asis'}
if (!exists("mnpflex")) mnpflex <- NULL
if (is.null(mnpflex) || !nrow(mnpflex)) {
  cat('<div class="note-muted">No MNP-Flex result available for this sample.</div>\n')
} else {
  cat('<div class="note">',
      'MNP-Flex is a platform-agnostic methylation classifier for',
      'sequencing-based methylation data. It is compatible with the Heidelberg',
      'CNS tumour methylation classifier v12.8 comprising 184 subclasses. The',
      'methylation bed file produced by this pipeline was submitted through the',
      '<a href="https://app.epignostix.com">Epignostix</a> platform API; the',
      'classifier and its quality check are reported as returned.',
      '</div>\n')
  cat('<div class="note-muted">',
      'Methylation classification of CNS tumours using MNP-Flex is a research',
      'tool currently under development. It has not been clinically validated in',
      'sufficiently large cohorts. Interpretation and implementation of the',
      'results in a clinical setting is in the sole responsibility of the',
      'treating physician.',
      '</div>\n')
  if (!is.na(mnpflex_clf)) cat('<div class="note-muted">Classifier: ', mnpflex_clf, '</div>\n')
  if (!is.na(mnpflex_qc))  cat('<div class="note-muted">', mnpflex_qc, '</div>\n')

  d <- head(mnpflex[order(-mnpflex$score), ], 10)
  names(d) <- c("Methylation class", "Score")
  print(kable(d, format = "html", escape = FALSE, row.names = FALSE, digits = 4) %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                        full_width = TRUE, font_size = 12) %>%
          row_spec(0, bold = TRUE, color = "white", background = "#0047b9"))
  cat('<div class="note-muted">',
      'Descriptions of the methylation classes are given in',
      '<a href="https://www.cell.com/cancer-cell/fulltext/S1535-6108(25)00495-7">',
      'Cancer Cell (2025)</a>.',
      '</div>\n')
}
```

</div>

<div class="section">

## MGMT promoter methylation \
<div class="note">
Average coverage of MGMT is: **`r cov`**x.
</div>

```{r setup2, echo=FALSE}
# The numeric MGMT status is the clinically relevant result; the methylartist
# plot is supplementary. Gate them separately so a failed plot does not hide
# a successful prediction.
show_mgmt <- mgmt_status == "true"
show_mgmt_plot <- methylartist_status == "true"
```

```{r conditional_block, echo=FALSE, results='asis', eval=show_mgmt}
mgmt_file <- read.csv(mgmt)
avg <- mgmt_file$average
avg <- round(as.numeric(avg), 2)
avg <- paste0(avg,"%")
status <- mgmt_file$status
cat('<div class="note-muted">MGMT promoter methylation status is assessed with a logistic regression model over the 137 most predictive CpG sites in the MGMT promoter region; the cutoff is 25%.</div>')
cat('<div class="note">Average methylation = <strong>')
cat(avg)
cat('</strong></div><div class="note">Predicted MGMT promoter status = <strong>')
cat(status)
cat('</strong></div>')
```

```{r setup3, echo=FALSE}
mgmt_too_low <- FALSE
## if methylartist and mgmt exist
if (!file.exists(methylartist_plot) 
    & !file.exists(mgmt))
mgmt_too_low <- TRUE
```
```{r, echo=FALSE, warning=FALSE, results='asis', eval=mgmt_too_low}
cat('<div class="note-muted">MGMT promoter methylation status was not assessed in this sample due to sequence coverage at the MGMT promoter region being too low.</div>')
```

## MGMT promoter methylation plot
```{r, echo=FALSE, out.width="100%",warning=FALSE, eval=show_mgmt_plot}
knitr::include_graphics(methylartist_plot)
```

```{r, echo=FALSE, warning=FALSE, results='asis', eval=mgmt_too_low}
cat('<div class="note-muted">An MGMT promoter plot was not produced in this sample due to sequence coverage at the MGMT site being too low.</div>')
```

<div class="section">

## Structural variants

```{r, echo=FALSE, results='asis'}
if (!exists("fusions_df")) fusions_df <- NULL
if (is.null(fusions_df) || !nrow(fusions_df)) {
  cat('<div class="note">No fusion from the curated CNS list was detected.</div>\n')
} else {
  d <- data.frame(
    Fusion      = gsub("--", " \u2013 ", fusions_df$fusion),
    Type        = fusions_df$svtype,
    Breakpoints = paste0(fusions_df$chrom1, ":", format(as.numeric(fusions_df$pos1),
                         big.mark = ",", trim = TRUE), "  \u2192  ",
                         fusions_df$chrom2, ":", format(as.numeric(fusions_df$pos2),
                         big.mark = ",", trim = TRUE)),
    # kb below a megabase: intragenic events such as EGFRvIII are tens of kb
    Size        = ifelse(fusions_df$span == "." | is.na(fusions_df$span), "-",
                  ifelse(as.numeric(fusions_df$span) < 1e6,
                         paste0(round(as.numeric(fusions_df$span) / 1e3), " kb"),
                         paste0(round(as.numeric(fusions_df$span) / 1e6, 2), " Mb"))),
    Reads       = fusions_df$reads,
    VAF         = if (is.null(fusions_df$vaf)) "-" else fusions_df$vaf,
    Callers     = fusions_df$caller,
    Significance= fusions_df$significance,
    Association = fusions_df$entity,
    check.names = FALSE)
  print(kable(d, format = "html", escape = FALSE, row.names = FALSE) %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                        full_width = TRUE, font_size = 12) %>%
          row_spec(0, bold = TRUE, color = "white", background = "#0047b9"))
}
```

<h4>EGFRvIII</h4>

```{r, echo=FALSE, results='asis'}
if (!exists("egfrviii_df")) egfrviii_df <- NULL
if (is.null(egfrviii_df) || !nrow(egfrviii_df)) {
  cat('<div class="note">No EGFRvIII variant found.</div>\n')
} else {
  e <- data.frame(
    Deletion    = "EGFR exons 2–7 (potential)",
    Type        = egfrviii_df$svtype,
    Breakpoints = paste0(egfrviii_df$chrom, ":",
                         format(as.numeric(egfrviii_df$pos1), big.mark = ",", trim = TRUE),
                         "  →  ",
                         format(as.numeric(egfrviii_df$pos2), big.mark = ",", trim = TRUE)),
    Size        = paste0(round(as.numeric(egfrviii_df$span) / 1e3), " kb"),
    Reads       = egfrviii_df$reads,
    VAF         = egfrviii_df$vaf,
    Callers     = egfrviii_df$caller,
    check.names = FALSE)
  print(kable(e, format = "html", escape = FALSE, row.names = FALSE) %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                        full_width = TRUE, font_size = 12) %>%
          row_spec(0, bold = TRUE, color = "white", background = "#0047b9"))
}
```

<div class="note-muted">
Any call listed above is a potential EGFRvIII and must be confirmed against the
supporting reads in `sv/` before it is reported.
</div>

<div class="note-muted">
Fusions are screened against a curated list of recurrent CNS alterations. The
association column describes what a fusion is typically seen with; it is not a
diagnosis. The complete set of structural variants is written to `sv/`.
</div>

</div>

<div class="contact-section">
<div class="note-muted">
The Rapid CNS2 classification and report generation followed the protocol designed and published by Patel _et_ _al._ (2022) and Patel _et_ _al._ (2025).
</div>
<div class="note-muted">
Patel, A., Dogan, H., Payne, A., Krause, E., Sievers, P., Schoebe, N., Schrimpf, D., Blume, C., Stichel, D., Holmes, N., Euskirchen, P., Hench, J., Frank, S., Rosenstiel-Goidts, V., Ratliff, M., Etminan, N., Unterberg, A., Dieterich, C., Herold-Mende, C., Pfister, S. M., … Sahm, F. (2022). Rapid-CNS^2^: rapid comprehensive adaptive nanopore-sequencing of CNS tumors, a proof-of-concept study. _Acta_ _neuropathologica_, _143_(5), 609–612. https://doi.org/10.1007/s00401-022-02415-6
</div>
<div class="note-muted">
Patel, A., Göbel, K., Ille, S. et al. Prospective, multicenter validation of a platform for rapid molecular profiling of central nervous system tumors. *Nature Medicine* 31, 1567–1577 (2025). [https://doi.org/10.1038/s41591-025-03562-5](https://www.nature.com/articles/s41591-025-03562-5)
</div>
<div class="note-muted">
**The information contained with this report is intended for research use only and is not for use in diagnostic procedures.**
</div>

<div class="contact">
For any questions, please contact:
</div>
<div class="contact">
**Areeba Patel, PhD**
</div>
<div class="contact">
Department of Neuropathology, German Cancer Research Center
</div>
<div class="contact">
a.patel@kitz-heidelberg.de
</div>

<div class="note-muted">
Report generated on `r format(Sys.time(), '%d %B, %Y at %H:%M')`
</div>
</div>

<div class="footer">
  Generated using Rapid-CNS² pipeline - RESEARCH USE ONLY
</div> 